Tampering Detection In Low-Power Smart Cameras

### 2015-05-28 paper.tex
aggiunta frase nell'intro

We here introduce a tampering-detection algorithm that has been specifically designed for low-power smart cameras: the algorithm leverages very simple indicators that are then monitored by an outlier-detection scheme. Any frame yielding anomalous indicator is detected as a tampering attempt. Core of the algorithm is the partitioning of the scene into adaptively defined regions, that are preliminarily defined by segmenting the image during the algorithm-configuration phase, and which shows to substantially improve the detection of camera displacements. Our experiments show that the proposed algorithm can successfully operate on sequences acquired at very low-frame rate, such as one frame every minute, and at a very small computational complexity. %and leveraging the image partitioning into regions yields improved performance with respect to monitoring the whole scene

@@

%What are the key components of my approach and results? Also include any specific limitations.
\gi{AGGIUNGERE qualcosa su one-shot monitoring}
We present an algorithm to detect both camera defocus and displacement, as stated in Section \ref{sec:probForm}. The algorithm presented in Section~\ref{sec:propSol} relies on two indicators: the average image intensity to detect displacement, and the average gradient norm, to detect blur. These indicators can be easily computed and monitored by an outlier-detection technique to detect the corresponding tampering. We show that displacement-detection performance can be improved by preliminarily partitioning the scene into nonoverlapping regions, and then separately computing and monitoring the average intensity over different regions (Section \ref{subsec:Segmentation}). Remarkably, these regions can be defined during an initial configuration phase, thus separately monitoring different regions have a negligible computational overhead w.r.t. monitoring the whole image. Experiments in Section \ref{sec:experiments} show that operating on image regions can substantially improve the detection of camera displacements. % Concluding remarks and discussions are given in Section \ref{sec:Conclusion}.

>>>>

We here introduce a tampering-detection algorithm specifically designed for low-power smart cameras: the algorithm leverages very simple indicators that are then monitored by an outlier-detection scheme. Any frame yielding anomalous indicator is detected as a tampering attempt. Core of the algorithm is the partitioning of the scene into adaptively defined regions, that are preliminarily defined by segmenting the image during the algorithm-configuration phase, and which shows to substantially improve the detection of camera displacements. Our experiments show that the proposed algorithm can successfully operate on sequences acquired at very low-frame rate, such as one frame every minute, with a very small computational complexity. %and leveraging the image partitioning into regions yields improved performance with respect to monitoring the whole scene

@@

%What are the key components of my approach and results? Also include any specific limitations.
We here address the detection of camera blurring and displacement, which are presented in Section \ref{sec:probForm}. The proposed algorithm, detailed in Section~\ref{sec:propSol}, relies on two indicators: the average image intensity to detect displacement, and the average gradient norm, to detect blurring. These indicators can be easily computed and monitored by an outlier-detection technique in a low-power smart camera, thus our solution is meant as a very prompt trigger to be possibly combined with other sequential monitoring techniques. In particular, we show that separately monitoring the indicators over different regions of the scene can substantially improve the displacement-detection performance. Remarkably, these regions can be preliminarily defined during an initial configuration phase (Section \ref{subsec:Segmentation}), thus the algorithm operates at a negligible computational overhead w.r.t. monitoring the whole image. Experiments in Section \ref{sec:experiments} show that leveraging image regions can substantially improve the displacement-detection performance. % Concluding remarks and discussions are given in Section \ref{sec:Conclusion}.
